Digitization of the Australian Parliamentary Debates (1901-2022)^[Code is available at: https://github.com/lindsaykatz/hansard-proj]

### 2022-11-28 paper/paper.qmd
new url doc and updated script

A number of papers exist which utilize components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to explore the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

# plot of number of sitting days per month from 2015-2020
# all_files %>% 
#   filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
#   mutate(month_abb = month.abb[month]) %>% 
#   group_by(year, month_abb) %>% 
#   summarise(avg_days = n()) %>% 
#   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
#   geom_col() + 
#   facet_wrap(~year) +
#   theme_bw() + 
#   labs(x = "Month", 
#        y="Count", 
#        title = "Number of sitting days per month (2015-2020)") +
#   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
```

@@

plot2 <- fedchamb_rows %>% 
  mutate(year = as.numeric(str_extract(date, "\\d\\d\\d\\d(?=-)"))) %>% 
  filter(year!=2022) %>% 
  group_by(year, fedchamb_flag) %>% 
  summarise(avg_rows = mean(n_rows)) %>% 
  ggplot(aes(y = avg_rows, x = as.factor(year), fill = fedchamb_flag)) + 
  geom_bar(position = "stack", stat = "identity") +
  theme_bw() +
  labs(x = "Year", y = "Average number of rows", fill = "") +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))

>>>>

A number of papers exist which utilize components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to explore the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

# plot of number of sitting days per month from 2015-2020
# all_files %>% 
#   filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
#   mutate(month_abb = month.abb[month]) %>% 
#   group_by(year, month_abb) %>% 
#   summarise(avg_days = n()) %>% 
#   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
#   geom_col() + 
#   facet_wrap(~year) +
#   theme_bw() + 
#   labs(x = "Month", 
#        y="Count", 
#        title = "Number of sitting days per month (2015-2020)") +
#   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))

#plot1 + ggtitle("Total number of sitting days per year (2000-2021)")
```

@@

plot2 <- fedchamb_rows %>% 
  mutate(year = as.numeric(str_extract(date, "\\d\\d\\d\\d(?=-)"))) %>% 
  filter(year!=2022) %>% 
  group_by(year, fedchamb_flag) %>% 
  summarise(avg_rows = mean(n_rows)) %>% 
  ggplot(aes(y = avg_rows, x = as.factor(year), fill = fedchamb_flag)) + 
  geom_bar(position = "stack", stat = "identity") +
  theme_bw() +
  labs(x = "Year", y = "Average number of rows", fill = "")
